Acid-induced protein gels: from gelation to stress-induced failure

### 2015-10-16 fig_plis/supplementary_plis.tex
Talk ontpellier Ajoute dosage

>>>>

Combining equations~(\ref{eq:sigma0P}) and (\ref{eq:qP}) we obtain the minimal stress to observe buckling
\begin{equation}
\sigma_\parallel = \frac{h}{H}  B  \left(\frac{24}{\Upsilon}\right)^{1/3}.
\end{equation}

Let us compare $\sigma_\parallel$ to the stress induced by swelling $\sigma_s$ for a sample abiding to Poiseuille model: sample c in Table~\ref{tab:data}. From the previous equation, we obtain $\sigma_\parallel \approx \SI{9}{\pascal}$. On the other hand, we estimate $\sigma_s = B\gamma$ where $\gamma$ is the strain induced by swelling. For the same sample, Figure \ref{M-fig:sideview}c gives us the excess area $\epsilon$ as a function of time. The first reliable measure of $\gamma = \sqrt{\epsilon}$ after buckling is 2.5\% at $t=\SI{35}{\minute}$. Therefore, the stress induced by swelling is $\sigma_s \approx \SI{35}{\pascal}$, indeed sufficient to cause buckling.

### 2015-10-16 talk_Montpellier.tex
Talk ontpellier Ajoute dosage

\institute[E.N.S. Lyon]{Laboratoire de physique, Ecole Normale Sup\'{e}rieure de Lyon}
\title[Yoghurt under stress]{Acid-induced protein gels: from gelation to stress-induced failure}
\author[M. Leocmach]{Mathieu Leocmach}
\date{10 June 2015}
\titlegraphic{
	\includegraphics[height=2\baselineskip,clip=true, trim=6mm 14mm 6mm 0]{NEW-Logo-ERC-OUTLINE}\quad
	\includegraphics[height=2\baselineskip]{logo_ums_grand}\quad
	\includegraphics[height=2\baselineskip]{CNRSfilaire-Q}\quad
	\includegraphics[height=2\baselineskip]{logo_ens-lyon}
	}

@@

%\tikzset{external/force remake}
\begin{frame}{The simplest yoghurt}
\begin{block}{Acid-set protein gel}
\begin{itemize}
\item Water (\SI{30}{\celsius})
\item Sodium caseinate (milk protein) 4\%
\raisebox{0.6\normalbaselineskip}[0pt][0pt]{$\left.\rule{0pt}{1.1\normalbaselineskip}\right\}$ stable solution}
\item Glucono-$\delta$-lactone (GDL) 1\% $\Rightarrow$ slow homogeneous acidification
\end{itemize}
\end{block}

@@

\begin{frame}{Merciless yoghurt breakers}
\textit{Leocmach et al. PRL 113, 038303 (2014), \footnotesize ArXiv 1401.8234}

\bigskip
\begin{tabu}{X[c]X[c]c}
\includegraphics[height=0.3\textheight]{Chris}&
\includegraphics[height=0.3\textheight]{Thibaut}&
\includegraphics[height=0.3\textheight]{Seb}\\
Christophe Perge & Thibaut Divoux & Sebastien Manneville\\
PhD student & CNRS researcher & Professor\\
E.N.S. Lyon &  CRPP Bordeaux & E.N.S. Lyon\\
\end{tabu}

\bigskip
\begin{description}[Special thanks]
\item[Special thanks] to Alan Parker (Firmenich) for prompting this study and providing casein \& GDL
\end{description}

\end{frame}

>>>>

\institute[iLM]{Institut Lumière Matière, Lyon, France}
\title[Yoghurt under stress]{Acid-induced protein gels: from gelation to stress-induced failure}
\author[M. Leocmach]{Mathieu Leocmach}
\date{10 June 2015}
\titlegraphic{
	\begin{tabu}{X[c]X[c]X[c]X[c]}
		\includegraphics[height=3\baselineskip]{Chris}&
		\includegraphics[height=3\baselineskip]{Thomas}&
		\includegraphics[height=3\baselineskip]{Thibaut}&
		\includegraphics[height=3\baselineskip]{Seb}\\
		Christophe Perge & Thomas\linebreak Gibaud & Thibaut\linebreak Divoux & Sebastien Manneville\\
	\end{tabu}

	\vfill
	\includegraphics[height=2\baselineskip]{logo_ens-lyon}\quad
	\includegraphics[height=2\baselineskip]{logo_ums_grand}\quad
	\includegraphics[height=2\baselineskip]{CNRSfilaire-Q}\quad
	\includegraphics[height=2\baselineskip]{CRPP}\quad
	\includegraphics[height=2\baselineskip,clip=true, trim=6mm 14mm 6mm 0]{NEW-Logo-ERC-OUTLINE}
	}

@@

%\tikzset{external/force remake}
\begin{frame}{The simplest yoghurt}
\begin{block}{Acid-set protein gel}
\begin{itemize}
\item Water (\SI{30}{\celsius})
\item Sodium caseinate (milk protein) 4\%
\raisebox{0.6\normalbaselineskip}[0pt][0pt]{$\left.\rule{0pt}{1.1\normalbaselineskip}\right(\}$ stable solution}
\item Glucono-$\delta$-lactone (GDL) 1\% $\Rightarrow$ slow homogeneous acidification
\end{itemize}
\end{block}

@@

\section*{Beyond critical gels}

\begin{frame}{Acidifying casein solutions with \textup{HCl}}
\tikzsetnextfilename{dosage}
\input{fig_presentation/dosage.pgf}
\end{frame}

%\begin{frame}{Merciless yoghurt breakers}
%\textit{Leocmach et al. PRL 113, 038303 (2014), \footnotesize ArXiv 1401.8234}
%
%\bigskip
%\begin{tabu}{X[c]X[c]c}
%\includegraphics[height=0.3\textheight]{Chris}&
%\includegraphics[height=0.3\textheight]{Thibaut}&
%\includegraphics[height=0.3\textheight]{Seb}\\
%Christophe Perge & Thibaut Divoux & Sebastien Manneville\\
%PhD student & CNRS researcher & Professor\\
%E.N.S. Lyon &  CRPP Bordeaux & E.N.S. Lyon\\
%\end{tabu}
%
%
%\bigskip
%\begin{description}[Special thanks]
%\item[Special thanks] to Alan Parker (Firmenich) for prompting this study and providing casein \& GDL
%\end{description} 
%
%\end{frame}
